A Bayesian approach to burial networks to infer social changes in northeastern Taiwan during the European colonization period

### 2021-01-11 analysis/paper/paper.Rmd
get the caching working as expected with correct file paths for the md5sum fn

```{r import-and-inspect-data, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("000-prep1-value-burials.R"))}
suppressWarnings(source(here::here("analysis", "paper", "000-prep1-value-burials.R")))
```

```{r tidy-data, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("001-data-tidy.R"))}
suppressWarnings(source(here::here("analysis", "paper", "001-data-tidy.R")))
```

@@

```{r burial-location, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("002-burial-location.R"))}
suppressWarnings(source(here::here("analysis", "paper", "002-burial-location.R")))
```

@@

```{r bergm-pre, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("003-burials-pre-network-modelling.R"))}
suppressWarnings(source(here::here("analysis", "paper", "003-burials-pre-network-modelling.R")))
```

```{r bergm-post, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("004-burials-post-network-modelling.R"))}
suppressWarnings(source(here::here("analysis", "paper", "004-burials-post-network-modelling.R")))
```

@@

```{r network-diagrams, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("005-network-diagrams-two-phases.R"))}
suppressWarnings(source(here::here("analysis", "paper", "005-network-diagrams-two-phases.R")))
```

@@

```{r posterior-distribution, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("006-bergm-distribution-stats.R"))}
suppressWarnings(source(here::here("analysis", "paper", "006-bergm-distribution-stats.R")))
```

<!--posterior stats for pre-E-->
We examine the estimates from the posterior distributions to compare their differences in structure of the simulated networks (Table \@ref(tab:table-posterior-stats); Figure \@ref(fig:figure-posterior-distribution)). For the pre-European network simulations, the nodal covariates, ritual-homophily, have significant effects on the formation of relations between burials. The positive effect demostrates that burials with ritual pottery tend to form relations. Despite positive values for some covariates, such as age-homophily, sex-homophily and burial value-homophily, they do not show a significant tendency to form relations duo to value of zero in the confidence intervals. Similarly, the dyadic covariate, physical distance, shows no significant effect, indicating that physical proximity between burials does not affect the formation of relations. For the endogenous network effects, transitivity (gwesp) present significant positive effect, while popularity (gwdegree) demonstrates negative effect. The high positive value for transitivity suggests a tendency of burials to be clustered in closed transitive structures, indicative of the presence of multiple corporate groups sharing burial goods in common. The negative popularity shows there is a tendency toward decentralization that reflects most burials have similar number of ties without any prominent ones. This might imply that individuals have equal access to trade goods in terms of the flow of goods.

@@

```{r bootstrap-CI-test, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("007-bootstrap-CI.R"))}
suppressWarnings(source(here::here("analysis", "paper", "007-bootstrap-CI.R")))
```

@@

```{r bootstrap-t-test, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("008-bootstrap-t-test.R"))}
suppressWarnings(source(here::here("analysis", "paper", "008-bootstrap-t-test.R")))
pval_den <- signif(density_b_test$p.value, 4)
pval_trans <- signif(trans_b_test$p.value, 4)
pval_star <- signif(star_b_test$p.value, 4)
```

>>>>

```{r import-and-inspect-data, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/000-prep1-value-burials.R"))}
suppressWarnings(source(here::here("analysis", "paper", "000-prep1-value-burials.R")))
```

```{r tidy-data, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/001-data-tidy.R"))}
suppressWarnings(source(here::here("analysis", "paper", "001-data-tidy.R")))
```

@@

```{r burial-location, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/002-burial-location.R"))}
suppressWarnings(source(here::here("analysis", "paper", "002-burial-location.R")))
```

@@

```{r bergm-pre, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/003-burials-pre-network-modelling.R"))}
suppressWarnings(source(here::here("analysis", "paper", "003-burials-pre-network-modelling.R")))
```

```{r bergm-post, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/004-burials-post-network-modelling.R"))}
suppressWarnings(source(here::here("analysis", "paper", "004-burials-post-network-modelling.R")))
```

@@

```{r network-diagrams, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/005-network-diagrams-two-phases.R"))}
suppressWarnings(source(here::here("analysis", "paper", "005-network-diagrams-two-phases.R")))
```

@@

```{r posterior-distribution, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/006-bergm-distribution-stats.R"))}
suppressWarnings(source(here::here("analysis", "paper", "006-bergm-distribution-stats.R")))
```

<!--posterior stats for pre-E-->
We examine the estimates from the posterior distributions to compare their differences in structure of the simulated networks (Table \@ref(tab:table-posterior-stats); Figure \@ref(fig:figure-posterior-distribution)). For the pre-European network simulations, the nodal covariates, ritual-homophily, have significant effects on the formation of relations between burials. The positive effect demonstrates that burials with ritual pottery tend to form relations. Despite positive values for some covariates, such as age-homophily, sex-homophily and burial value-homophily, they do not show a significant tendency to form relations duo to value of zero in the confidence intervals. Similarly, the dyadic covariate, physical distance, shows no significant effect, indicating that physical proximity between burials does not affect the formation of relations. For the endogenous network effects, transitivity (gwesp) present significant positive effect, while popularity (gwdegree) demonstrates negative effect. The high positive value for transitivity suggests a tendency of burials to be clustered in closed transitive structures, indicative of the presence of multiple corporate groups sharing burial goods in common. The negative popularity shows there is a tendency toward decentralization that reflects most burials have similar number of ties without any prominent ones. This might imply that individuals have equal access to trade goods in terms of the flow of goods.

@@

```{r bootstrap-CI-test, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/007-bootstrap-CI.R"))}
suppressWarnings(source(here::here("analysis", "paper", "007-bootstrap-CI.R")))
```

@@

```{r bootstrap-t-test, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/008-bootstrap-t-test.R"))}
suppressWarnings(source(here::here("analysis", "paper", "008-bootstrap-t-test.R")))
pval_den <- signif(density_b_test$p.value, 4)
pval_trans <- signif(trans_b_test$p.value, 4)
pval_star <- signif(star_b_test$p.value, 4)
```
